### 2014-07-11 paper/introduction.tex
change statements about prior art

Recently, human-computer interaction researchers have begun to explore how to prototype interactive objects using additive 3D printing processes.
\changes{Existing approaches, including Printed Optics \cite{Willis-printedoptics} and Sauron \cite{Savage-sauron}, exclusively focus on optical sensing and visual displays --- we seek to grow the vocabulary of supported tangible input and output modalities, and we propose using pipes and cavities, allowing designers to integrate secondary materials post-print, for this purpose.}

>>>>

Recently, human-computer interaction researchers have begun to explore how to prototype interactive objects using additive 3D printing processes.
\changes{Some existing approaches, including Printed Optics \cite{Willis-printedoptics} and printing teddy bears \cite{Hudson-bears} create one-off designs for interactive devices by using high-end or custom printers which to fabricate materials that are clear or soft.  Others, like Sauron \cite{Savage-sauron}, offer design tools but focus on visual input and display-based output --- we seek to grow the input and output modalities available to makers.  We propose using pipes and cavities, allowing integration of secondary materials post-print, for this purpose.}
